More than one Author with different Affiliations

### 2016-01-13 manuscript.tex
nothing to se ehere
addressed figure comments

A number of tools have recently been published to handle high throughput sequencing data \citep{garrigan2013popbam, purcell2007plink, danecek2011variant, hutter2006genome}, but the majority of these either make limiting assumptions about the data (e.g., all sites have been sequenced, all genomes are haploid, sequencing is to sufficient depth, all individuals are outcrossing) or are specialized tools offering a narrow set of analysis options. 
Korneliussen et al. \citep{korneliussen2014angsd} recently published the software package ANGSD, which enables users to flexibly perform a large number of common population genetic analyses, including diversity statistics, admixture analysis including Patterson's D statistic \citep{Durand:2011jd}, site frequency spectrum estimation \citep{pmid22911679}, and neutrality test statistics \citep{korneliussen_calculation_2013}.\jri{are all these within ANGSD or are some ngsPopgen?}
One of the most important features of ANGSD is that most analyses are performed directly on genotype likelihoods, freeing users from the requirement of calling variants or genotypes and permitting analysis of low-coverage data or sequences with large amounts of missing data.

@@

\begin{table}
\begin{center}
    \begin{tabular}{ | l | p{5cm} |}
    \hline
    \textbf{Methods Implemented} & \textbf{Interactive Graphing} \\ \hline \hline
    Patterson's D (ABBA-BABA) & Yes \\ \hline
    Admixture & Yes  \\ \hline
    Ancestral Sequence & No \\ \hline
    Genotype Likelihoods & No \\ \hline
    Inbreeding Coefficients & No \\ \hline
    PCA & Yes \\ \hline
    Site Frequency Spectrum & Yes \\ \hline
    Diversity Statistics  & Yes \\ \hline
    \end{tabular}
    \caption{Table of methods implemented in ANGSD-wrapper}
    \label{tab:methods}
    \end{center}
\end{table}
\jri{list diversity statistics in parentheses. what about Fst?}

@@

In order to use the plotting software, the user navigates to the desired tab and uploads the appropriate file of results. 
The Shiny server automatically parses ANGSD output files and creates the resulting plot(s) (Figure \ref{fig:theta}), which can be saved using the browser's built in image saving capabilities. \jri{add genes from gff. i don't think it's Mb 1-10, pls check. if so, is x-axis wrong?}

\begin{figure}
\centering
\includegraphics[width=130mm]{figures/ThetasPlot.png}
\caption{A visualization of Watterson's $\theta$ estimated by ANGSD across the first 10 megabases of chromosome 10 in {\it Zea mays} spp. {\it mays} using ANGSD-wrapper\label{fig:theta} }
\end{figure}

\section*{Example data}
\jri{show k=2 and k=3 for adxmxture in supp.}
\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/MainTextWorkflow.pdf}
\caption{Example analysis workflow diagram.}
\label{fig:workflow}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/figure3big.pdf}
\caption{Summary statistics for {\it Zea mays}. Site frequency spectra for A. maize and B. teosinte. C. distribution of pairwise differences for maize (blue) and teosinte (orange).}
\label{fig:figure3}
\end{figure}

@@

We first use \X\ to estimate the site frequency spectrum (SFS) of both maize and its wild progenitor \textit{Zea mays} ssp. \textit{parviglumis}, assuming an inbreeding coefficient of $F=1$ since these are all highly inbred samples. \jri{do we worry that fig. 3 not graphs directly from A-W?}

>>>>

A number of tools have recently been published to handle high throughput sequencing data \citep{garrigan2013popbam, purcell2007plink, danecek2011variant, hutter2006genome}, but the majority of these either make limiting assumptions about the data (e.g., all sites have been sequenced, all genomes are haploid, sequencing is to sufficient depth, all individuals are outcrossing) or are specialized tools offering a narrow set of analysis options. 
Korneliussen et al. \citep{korneliussen2014angsd} recently published the software package ANGSD, which enables users to flexibly perform a large number of common population genetic analyses, including diversity statistics, admixture analysis including Patterson's D statistic \citep{Durand:2011jd}, site frequency spectrum estimation \citep{pmid22911679}, and neutrality test statistics \citep{korneliussen_calculation_2013}. %\jri{are all these within ANGSD or are some ngsPopgen?} all are in ANGSD
One of the most important features of ANGSD is that most analyses are performed directly on genotype likelihoods, freeing users from the requirement of calling variants or genotypes and permitting analysis of low-coverage data or sequences with large amounts of missing data.

@@

\begin{table}
\begin{center}
    \begin{tabular}{ | p{5cm} | p{5cm} |}
    \hline
    \textbf{Methods Implemented} & \textbf{Interactive Graphing} \\ \hline \hline
    Patterson's D (ABBA-BABA) & Yes \\ \hline
    Admixture & Yes  \\ \hline
    Ancestral Sequence & No \\ \hline
    Genotype Likelihoods & No \\ \hline
    Inbreeding Coefficients & No \\ \hline
    PCA & Yes \\ \hline
    Site Frequency Spectrum & Yes \\ \hline
    Diversity Statistics ($\theta_w$, $\theta_\pi$, Fu and Li's $\theta$, Fay's $\theta$)   & Yes \\ \hline
    Neutrality Test Statistics (Tajima's D, Fu and Li's D, Fu and Li's F,  Fay and Wu's H, Zeng's E ) & Yes \\ \hline
    Fst & Yes \\ \hline
    \end{tabular}
    \caption{Table of methods implemented in ANGSD-wrapper}
    \label{tab:methods}
    \end{center}
\end{table}
%\jri{in table: list diversity statistics in parentheses. what about Fst?} done. and added Neutrality test stats

@@

In order to use the plotting software, the user navigates to the desired tab and uploads the appropriate file of results. 
The Shiny server automatically parses ANGSD output files and creates the resulting plot(s) (Figure \ref{fig:theta}), which can be saved using the browser's built in image saving capabilities. % \jri{add genes from gff. i don't think it's Mb 1-10, pls check. if so, is x-axis wrong?} done

\begin{figure}
\centering
\includegraphics[width=130mm]{figures/fig1.png}
\caption{A visualization of Watterson's $\theta$ estimated by ANGSD across a 1.5 megabase region of chromosome 10 in {\it Zea mays} spp. {\it mays} using ANGSD-wrapper. Blue boxes indicate genic regions provided by a GFF annotation. \label{fig:theta} }
\end{figure}

\section*{Example data}
% \jri{show k=2 and k=3 for adxmxture in supp.} done
\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/MainTextWorkflow.pdf}
\caption{Example analysis workflow diagram.}
\label{fig:workflow}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/figure3big.pdf}
\caption{Summary statistics for {\it Zea mays}. Site frequency spectra for A. maize and B. teosinte. C. distribution of pairwise differences for maize (blue) and teosinte (orange). Pairwise diversity results are visualized separately from the interactive graphics and colors were added to A and B using a custom script.}
\label{fig:figure3}
\end{figure}

@@

We first use \X\ to estimate the site frequency spectrum (SFS) of both maize and its wild progenitor \textit{Zea mays} ssp. \textit{parviglumis}, assuming an inbreeding coefficient of $F=1$ since these are all highly inbred samples. %\jri{do we worry that fig. 3 not graphs directly from A-W?} % noted this in the figure legend
